Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-02-06 ms.tex
minor clarifications and fixes.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing.
An illustrative sinusoidal function is plotted for comparison.
}\label{fig:CV3GrismSpecFringing}
\end{figure}

@@

The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the oscillations
For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
}\label{fig:CV3GrismSpecFringing}
\end{figure}

@@

The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the position oscillations.
For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
